\addcontentsline{toc}{chapter}{\bibname}

\begin{thebibliography}{9}
\bibitem{latexcompanion}
Michel Goossens, Frank Mittelbach, and Alexander Samarin.
\textit{The \LaTeX\ Companion}.
Addison-Wesley, Reading, Massachusetts, 1993.

\bibitem{einstein}
Albert Einstein.
\textit{Zur Elektrodynamik bewegter K{\"o}rper} . (German)
[\textit{On the electrodynamics of moving bodies}].
Annalen der Physik, 322(10):891–921, 1905.

\bibitem{knuthwebsite}
Knuth: Computers and Typesetting,
\\\texttt{http://www-cs-faculty.stanford.edu/\~{}uno/abcde.html}
\end{thebibliography}

AV:
https://github.com/alicevision/AliceVision
%https://alicevision.org/#photogrammetry
https://github.com/alicevision/meshroom-manual

SIFT:
[Distinctive Image Featuresfrom Scale-Invariant Keypoints]
https://www.cs.ubc.ca/~lowe/papers/ijcv04.pdf

[Anatomy of the SIFT Method]
http://www.ipol.im/pub/art/2014/82/

[OpenCV]
%https://opencv-python-tutroals.readthedocs.io/en/latest/py_tutorials/py_feature2d/py_sift_intro/py_sift_intro.html

Python 3.7:
https://matplotlib.org/
https://docs.python.org/3/library/argparse.html
https://docs.python.org/3/library/json.html

SfM:
P. Moulon, P. Monasse and R. Marlet. Adaptive Structure from Motion with a contrario model estimation. ACCV 2012.

M. Jancosek, T. Pajdla. Multi-view reconstruction preserving weakly-supported surfaces. CVPR 2011.



?:
SIFT:
https://aishack.in/tutorials/sift-scale-invariant-feature-transform-introduction/
https://medium.com/analytics-vidhya/introduction-to-sift-scale-invariant-feature-transform-65d7f3a72d40

%https://en.wikipedia.org/wiki/Scale-invariant_feature_transform
%https://commons.wikimedia.org/wiki/File:Sift_keypoints_filtering.jpg?uselang=ru
DoG:
http://aragorn.pb.bialystok.pl/~boldak/DIP/CPO-W04-v01-50pr.pdf
